%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 2pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%\documentclass[margin, 2pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

%\usepackage[margin=0.8in]{geometry}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{enumitem}

\setlength{\textwidth}{5.2in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\LARGE\bf Chetan Nagaraj Naik} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{350 Circle Rd., Stony Brook, NY 11790} % Your address
\moveleft.5\hoffset\centerline{cnaik@cs.stonybrook.edu}%, (631) 974-8046}
\moveleft.5\hoffset\centerline{(631) 974-8046}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
% \section{OBJECTIVE}  

% A position in the field of computers with special interests in business applications programming, information processing, and management systems. 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Master of Science,} Computer Science \hfill Aug. 2014 $-$ May. 2016\\
Stony Brook University, Stony Brook, NY. \hfill (expected)\\
%Courses: Data Science, Data Mining meets Graph Mining, Computer Vision, Analysis of Algorithms.\\
GPA: 3.48/4

{\sl Bachelor of Engineering,} Electronics \& Communications \hfill Aug. 2007 $-$ Jun. 2011\\
R. V. College of Engineering, Bangalore, India.\\
CGPA: 8.67/10
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{WORK EXPERIENCE}

{\sl Research Assistant} \hfill Jan 2015 $-$ Present \\
Natural Language Processing Lab, Stony Brook University

\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Developing a question answering system that can recognize instances of processes. The system can automatically identify the key semantic roles and use them in an alignment framework to answer $4^{th}$ grade process recognition questions.
\end{itemize}


{\sl Analyst} \hfill July 2011 $-$ May 2014 \\
Google India Pvt. Ltd., Hyderabad, India 

\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Developed and launched a ad-click spam filter which addresses one of the most pressing click fraud problems.
  		It  has an impact of around \$1 million a month.
  \item Designed and developed metrics infrastructure for the global team of 50 analysts.
  \item Developed a method based on Pearson correlation coefficient for histogram similarity search.
  		This helps Google detect fraudulent publisher accounts and prevent millions of dollars worth of damages
        to advertisers.
%  \item Built a scalable system called `Watergate' that allows a consistent, streamlined, and collaborative process to
%  		enable additional features for publishers. The automation from this system helps the team save 350 full
%        time employee (FTE) hours per quarter.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS SECTION
%---------------------------------------------------------------------------------------- 

\section{ACADEMIC PROJECTS}

{\sl Question Answering System.} \hfill Feb. 2015 $-$ May. 2015

\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Built a question answering system that uses alignment over semantic roles to answer and pass a 4th grade science exam. The model has an accuracy of 62.5%\%.
\end{itemize}

{\sl Predicting Super Bowl and College Football champions.} \hfill Aug. 2014 $-$ Dec. 2014

\begin{itemize} \itemsep -2pt % Reduce space between items
  \item Built machine learning models to predict the winners of 2015 Super Bowl and College Football Championship. The model has an accuracy of 63\%.
\end{itemize}

{\sl Predicting rating stars of Yelp reviews from review text.} \hfill Aug. 2014 $-$ Dec. 2014

\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Built topic models using LDA and NMF along with sentiment layers to predict the review star rating from review text with 61\% accuracy.
\end{itemize}

{\sl Predicting facial beauty using CNN.} \hfill Aug. 2014 $-$ Dec. 2014

\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Designed and trained a Convolutional Neural Network (CNN) using Caffe (a fast framework for deep learning) to predict facial beauty without using landmark features. This model has an accuracy of 51\%.
\end{itemize}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{AWARDS} 
%- Received 2 PQO Gold Awards at Google.\\
%- Received Spot Bonus at Google for my work on histogram based similarity search.\\
%- Received 10 peer bonuses for helping out peers by going above and beyond work requirements.\\
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=*]
  \item[--] Received 2 PQO Gold Awards at Google.
  \item[--] Received Spot Bonus at Google for my work on histogram based similarity search.
  \item[--] Received 10 Peer Bonuses for helping out peers by going above and beyond work requirements.
\end{itemize}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{COMPUTER \\ SKILLS} 

{\sl Programming Languages:} 
Python, C, C++, Java. \\
{\sl Familiar with following technologies:} IPython, scikit-learn, MapReduce, Bigtable, Dremel, Tenzing, PowerDrill, ColumnIO, Protocol Buffers, Django, Matlab, HTML, CSS. 

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}